Loss recovery and tail loss performance in Multipath TCP

### 2016-12-10 main.tex
TCP comparison

>>>>

Figures ~\ref{t1p,t2p,t1pp} represent the comparison of MPTCP and TCP burst completion times for the two bursts from server to client.

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.9\textwidth,natwidth=578.16,natheight=433.62]{plots/T1P.pdf}
\caption{Single packet tail loss}\label{t1p}
\end{center}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.9\textwidth,natwidth=578.16,natheight=433.62]{plots/T2P.pdf}
\caption{Two packet tail loss}\label{t2p}
\end{center}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.9\textwidth, natwidth=578.16,natheight=433.62]{plots/T1PP.pdf}
\caption{Single packet tail loss together with probe loss}\label{t1pp}
\end{center}
\end{figure}
